Title here

### 2020-07-07 paper/paper.Rmd
match the color in the last example with geozoo color

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
p5 <- kol_cdf_1d_2var_better %>% explore_trace_interp() + ggtitle("search_better, seed 123456")
p6 <- kol_cdf_1d_2var_better_2 %>% explore_trace_interp() +  ggtitle("search_better, seed 12345")

@@

```{r 1d-2var-better-random, fig.asp=0.5, fig.cap = "\\label{1d-2var-better-random}Using search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed."}
kol_cdf_1d_2var_better_random %>% 
  explore_trace_interp() + 
  ylim(0, 0.25) + 
  theme(legend.position = "none") + 
  ggtitle("search_better_random")
```

>>>>

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
color <- RColorBrewer::brewer.pal(3, "Dark2")
p5 <- kol_cdf_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_color_manual(values = color[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_cdf_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_color_manual(values = color[1]) + ggtitle("search_better, seed 12345")

@@

```{r 1d-2var-better-random, fig.asp=0.5, fig.cap = "\\label{1d-2var-better-random}Using search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed."}
kol_cdf_1d_2var_better_random %>% 
  explore_trace_interp(col = 0) + 
  ylim(0, 0.25) + 
  scale_color_manual(values = color[3]) + 
  theme(legend.position = "none") + 
  ggtitle("search_better_random")
```
